R Markdown Features

### 2018-07-11 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

Include **R Code Chunks' Variables** in the body of text.

```{r}
alpha <- 1:3
text <- c("a", "b")
```

1. The numeric variable $\alpha =$ `r alpha[1]`.
    ```{yaml}
    # The numeric variable $\alpha =$ `r alpha[1]`.
    ```

2. The string variable $text =$ `r text[1]`.
    ```{yaml}
    # The string variable $text =$ `r text[1]`.
    ```

@@

### Classical Citation: **Author**, **year**, and **brackets** {-}
- `Some text [@Bib.ID].`
    - Some text [@RN9].

### In-text Citation: **Author (year)** {-}
- `@Bib.ID Some text`
    - @RN15 Some text

- `@Bib.ID [p. 20] Some text.`
    - @RN9 [p. 20] Some text.

### Year only: Suppress Author {-}
- `Some text [-@Bib.ID].`
    - Some text [-@RN9]

### Two Citations {-}
- `Some text [@Bib.ID1; @Bib.ID2].`
    -  Some text [@RN9; @RN15].

- Prefix & Suffix
    - `Text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
    -  Text [see @RN9 pp. 45; also, @RN15 ch. 2].

@@

<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" width=90%" height="440" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:0px; max-width: 100%;" allowfullscreen></iframe>

>>>>

Include **R Code Chunk Variables** in the body of text. This can be a really useful feature for writing thesis or research paper:

- No need to copy & paste the outcomes, such as the statistics. This greatly reduce the risk of error, and it also largely boosts efficiency.

- Automatically updates the results in the paper when the data are updated. This also boosts efficiency and, more importantly, increases the **reproducibility** of the research: you can be confident that the results come directly from the data (unless there are errors in the *code*, which can be 'seen', whereas **errors from copy-&-paste's are invisible**).

Below is a simple demonstration of this feature.

```{r}
tr1 <- rnorm(n=25, mean=1.1) #data of treatment1
tr2 <- rnorm(n=25, mean=0.9) #data of treatment2
ttest <- t.test(tr1, tr2, paired = T)
diff <- ttest[["estimate"]][["mean of the differences"]]
p_val <- ttest[["p.value"]]
```

1. The mean difference between the two groups is `r round(diff, 3)`.
    ```{latex}
    The mean difference between the two treatments is `r round(diff, 3)`.
    ```

2. The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
    ```{latex}
        The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
    ```

@@

### Classical Citation: **Author**, **year**, and **brackets** {-}
- `Some text [@citekey].`
    - Some text [@RN9].

### In-text Citation: **Author (year)** {-}
- `@citekey Some text`
    - @RN15 Some text

- `@citekey [p. 20] Some text.`
    - @RN9 [p. 20] Some text.

### Year only: Suppress Author {-}
- `Some text [-@citekey].`
    - Some text [-@RN9]

### Two Citations {-}
- `Some text [@citekey1; @citekey2].`
    -  Some text [@RN9; @RN15].

- Prefix & Suffix
    - `Text [see @citekey1 pp.45; also, @citekey2 ch. 2].`
    -  Text [see @RN9 pp. 45; also, @RN15 ch. 2].

@@

<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" height="400px" width="100%" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:0px; max-width: 100%;" allowfullscreen></iframe>
